Proportions of extreme values the unusual direction

### 2021-04-13 analysis/reports/submission2/table1_extreme_values.Rmd
reorganize branch

all_results <- left_join(diss_results, skew_results) %>%
  left_join(metric_results)
# 
# cols1 <- c("Dataset", "High dissimilarity", "High proportion of rare species", "High skew", "Low Simpson", "Low Shannon")
# 
# all_results %>%
#   select(cols1)

cols2 <- c("Dataset", "Low proportion of rare species", "Low skew", "High Simpson", "High Shannon")

all_results %>%
  select(cols2)

@@

**Table ST5.** Proportions of extreme values for percentile scores for observed SADs compared to samples from the feasible set, for the less-usual direction of effects. This is the proportion of scores <2.5 or >97.5; by chance ~2.5% of scores should be in either extreme. n refers to the number of communities included for each dataset for each metric.

>>>>

all_results <- left_join(diss_results, skew_results) %>%
  left_join(metric_results)

cols1 <- c("Dataset", "High dissimilarity", "High proportion of rare species", "High skew", "Low Simpson", "Low Shannon")

all_results %>%
  select(cols1)

# 
# cols2 <- c("Dataset", "Low proportion of rare species", "Low skew", "High Simpson", "High Shannon")
# 
# all_results %>%
#   select(cols2)

@@

**Table 1.** Proportions of extreme values for percentile scores for observed SADs compared to samples from the feasible set. For dissimilarity, this is the proportion of percentile scores >95; by chance, ~5% of scores should be in this extreme. For all other metrics, this is the proportion <2.5 or >97.5; by chance ~2.5% of scores should be in either extreme. n refers to the number of communities included for each dataset for each metric.
